---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shinyClassifier

This Shiny application is a template of a multi-user image/text classification
tool designed for any scenario that involves a bunch of human coders classifying
a bunch of text or images. All it takes is a YAML config file and a CSV file 
with the content to-be-classified to construct an online multi-user 
classification system.

## Prerequisite

If you are deploying this dashboard on your own Shiny Server, please make sure
the following packages are installed:

* `shiny` (obviously)
* `shinydashboard`
* `shinyjs`
* `shinymanager`
* `DT`
* `purrr`
* `magrittr`

## Configure

You need to have two files ready: `config.yaml` and `data.csv`.

### `config.yaml`

All the basic configurations of your project goes here. The file itself is 
pretty self-explanatory so this section only focuses on setting up the users 
and questions.

For user details, you need to specify the username and password for each of the
users (aka human coders) involved in the project. You are strongly recommended 
to also set up an administrator account to keep track of the progress as well as
to mange the users later on.

```{yaml}
user:
  - user: admin
    password: admin
    admin: true
  - user: test
    password: test
    admin: false
```

Please note that you need to have all the users set up at this stage. It is
problematic to add any new user in the middle of the project period since the 
distribution of content to each user happens at the initialization stage.

The user details here will be stored in a SQLite database with the passwords
hashed. For security concern, you may want to assign dummy passwords here and
then change the passwords in the admin console, where you can also force users
to change their passwords upon the first log in.

Say your project is to find out whether an image has a human in it, and if so
what is the gender, the questions can be set up as follows:

```{yaml}
question:
  - text: Is there a human?
    value: human
    choice:
      - name: "Yes"
        value: 1
      - name: "No"
        value: 0
  - text: If there is, what is the gender?
    value: gender
    choice:
      - name: Not Applicable
        value: NA
      - name: Male
        value: M
      - name: Female
        value: F
```

The `text` and `name` entries are what the coders will see in the interface. 
The `value` entries are the variable names of your data. As with all variable
names in programming, you should avoid space and problematic symbols.

### `data.csv`

This CSV files should contain a column with name `data` containing the text or
links of the images to-be-classified.

## Initialization

Place `config.yaml` and `data.csv` in the root directory and run:

```{r, eval=FALSE}
source("initilize.R")
initialize_app()
```

This will parse the `config.yaml` file and create a `user.sqlite` storing the
user details and a `config.rda` containing the configurations of your project.

Afterwards, run:

```{r, eval=FALSE}
prep_data()
```

This will read `data.csv` and randomly and equally assign contents to each of 
the users (excluding admin accounts). Each user gets its own 
`data_<username>.rds` file with the content they are working on.

In the event where even distribution is not possible, the first few 
users will get one extra assigned content. For example, if there are 4000 images 
to be split within 3 coders, coder A and B will get 1667 images while coder C
will get 1666 images.

If you need all users to work on the same set of content (e.g. for inter-coder 
reliability test), run:

```{r, eval=FALSE}
prep_data(dist = FALSE)
```

## Using

Afterwards, the app is ready to be deployed. You can log into the admin account
to check the progress of each individual user. The classification results of
each user are stored in their respective `data_<username>.rds` files.
